Data 621---HW1---Regression Model---Version 2

### 2020-09-09 HW1/RegModel_Adler.Rmd
Model discussion

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
```{r loadPackages}
library(corrplot)
library(RColorBrewer)
library(ggplot2)
library(scales)
library(data.table)
```

@@

## Analysis
At this point we have a set of transformed independent variables on which we
can build a model. The target variable, `TARGET_WINS` does not need to be
scaled. Normally, we would have thrown everything into `caret`, but for the
purposes of this homework, we will use the `stepAIC` function from the `MASS`
package to perform a backwards-stepwise linear regression using AIC as our
goodness of fit metric. For ease, we will cast the dataset we were using from
tall back to wide first.

```{r lm1}
MBsc <- dcast(MBmeltSC, INDEX ~ Metric, value.var = 'Value')
```

@@

```{r loadPackages, echo=TRUE, eval=FALSE}
```
```{r readData, echo=TRUE, eval=FALSE}
```
```{r missingTable, echo=TRUE, eval=FALSE}
```
```{r summaryTable, echo=TRUE, eval=FALSE}
```
```{r boxPlot1, echo=TRUE, eval=FALSE}
```
```{r boxPlot2, echo=TRUE, eval=FALSE}
```
```{r corrgram, echo=TRUE, eval=FALSE}
```
```{r imputeMean, echo=TRUE, eval=FALSE}
```
```{r centerScale, echo=TRUE, eval=FALSE}
```
```{r plotScaled, echo=TRUE, eval=FALSE}
```
```{r boxCox, echo=TRUE, eval=FALSE}
```
```{r reScale, echo=TRUE, eval=FALSE}
```
```{r reImputeThenScale, echo=TRUE, eval=FALSE}
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
```{r loadPackages}
library(MASS)
library(corrplot)
library(RColorBrewer)
library(ggplot2)
library(scales)
library(data.table)
```

@@

## Analysis
Normally, we would have thrown everything into `caret`, but for the purposes of
this homework, we will use calls to base R for the null and saturated models and
the `stepAIC` function from the `MASS` package to perform a stepwise linear
regression using AIC as our goodness of fit metric.

At this point we have a set of transformed independent variables on which we
can build a model. The reasoning for the variable selection and transformations
are in previous sections. For ease, we will cast the dataset we were using from
tall back to wide first. Furthermore, the target variable, `TARGET_WINS` does
not need to be scaled.

We will show three models: the null model, the saturated model, and the model
resulting from the stepwise regression. For the regression, we will consider at
most pairwise interactions within the classes of metrics.

```{r lm, include=FALSE}
MBsc <- dcast(MBmeltSC, INDEX ~ Metric, value.var = 'Value')
# Replace TARGET_WINS with original. Could have restored it from MBmeltUnscale.
MBsc[, TARGET_WINS := MB[, TARGET_WINS]]
# Removing INDEX for convenience. Could have used "-INDEX" in the formula call.
MBsc[, INDEX := NULL]

nullModel <- lm(TARGET_WINS ~ 1, data = MBsc)
snm <- summary(nullModel)

saturatedModel <- lm(TARGET_WINS ~ ., data = MBsc)
ssm <- summary(saturatedModel)

stepModel <- stepAIC(saturatedModel, scope = list(upper = ~
  (TEAM_BASERUN_CS + TEAM_BASERUN_SB) ^ 2 + (TEAM_BATTING_2B + TEAM_BATTING_3B +
   TEAM_BATTING_BB + TEAM_BATTING_H + TEAM_BATTING_SO) ^ 2 + (TEAM_FIELDING_DP +
   TEAM_FIELDING_E) ^ 2 + (TEAM_PITCHING_BB + TEAM_PITCHING_H +
   TEAM_PITCHING_HR + TEAM_PITCHING_SO) ^ 2, lower = ~ 1), direction = 'both')

sstm <- summary(stepModel)
```
```{r nullOutput}
knitr::kable(snm$coefficients, digits = 3L,
             caption = 'Null Model Output')
```
The null model has an adjusted \(R^2\) of
`r prettyNum(snm$adj.r.squared, digits = 3L)` and an AIC of
`r prettyNum(AIC(nullModel), digits = 2L, big.mark = ',')`.

```{r satOutput}
knitr::kable(ssm$coefficients, digits = 3L,
             caption = 'Saturated Model Output')
```
The saturated model has an adjusted \(R^2\) of
`r prettyNum(ssm$adj.r.squared, digits = 3L)` and an AIC of
`r prettyNum(AIC(saturatedModel), digits = 2L, big.mark = ',')`.

```{r stepOutput}
knitr::kable(sstm$coefficients, digits = 3L,
             caption = 'Step Model with Pairwise Class Interactions Output')
```

The step model allowing pairwise interactions between the four classes of
metric: base running, batting, fielding, and pitching, has an adjusted \(R^2\)
of `r prettyNum(sstm$adj.r.squared, digits = 3L)` and an AIC of
`r prettyNum(AIC(stepModel), digits = 2L, big.mark = ',')`.

@@

```{r loadPackages, echo=TRUE, eval=FALSE}
```
```{r readData, echo=TRUE, eval=FALSE}
```
```{r missingTable, echo=TRUE, eval=FALSE}
```
```{r summaryTable, echo=TRUE, eval=FALSE}
```
```{r boxPlot1, echo=TRUE, eval=FALSE}
```
```{r boxPlot2, echo=TRUE, eval=FALSE}
```
```{r corrgram, echo=TRUE, eval=FALSE}
```
```{r imputeMean, echo=TRUE, eval=FALSE}
```
```{r centerScale, echo=TRUE, eval=FALSE}
```
```{r plotScaled, echo=TRUE, eval=FALSE}
```
```{r boxCox, echo=TRUE, eval=FALSE}
```
```{r reScale, echo=TRUE, eval=FALSE}
```
```{r reImputeThenScale, echo=TRUE, eval=FALSE}
```
```{r lm, echo=TRUE, eval=FALSE}
```
```{r nullOutput, echo=TRUE, eval=FALSE}
```
```{r satOutput, echo=TRUE, eval=FALSE}
```
```{r stepOutput, echo=TRUE, eval=FALSE}
```
